### 2016-11-28 local-capability-machine.tex
Changes to f2 proof

\begin{lemma}
  \label{lem:correctness-f2}
  For all $n \in \nats$
  let
    \var{offset-link-flag} & \defeq 2
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\var{offset-link-flag}) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\var{offset-link-flag},\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
    &\dom(\hs_{f2}) = [\mathtt{f2}-\var{offset-link-flag},\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  and
  \item The first address of $\hs_{f2}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f2}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  if 
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  then
    m'(\flag) = 0
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assunptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
    &(\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    &\quad(\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
Where 
  m''  \defeq \hs_{f2} \uplus 
        \ms_\link \uplus 
        \ms_\malloc \uplus 
        \ms_\stk' \uplus
        \ms_{\var{frame}}
Only the stack has changed
  \label{fig:f2-stack-before-adv}
$\start_\stk'':$   & $0$\\
$c_\stk',c_\stk'' \rightarrow$   & $c_\stk'$ \\
   & $c_{f2}'$ \\
$c_{\var{prp}} \rightarrow$   & Restore code \\
   & $1$\\
\begin{tabular}{r |c |}
$\pcreg$ & $\updatePcPerm{c_\adv}$\\
$r_0$  &  $c_{\var{prp}}$ \\
$r_1$ & $c_\adv$ \\
$r_{\var{stk}}$  & $c_{\var{stk}}'$ \\
& $0$ \\
\caption{Stack and register-file just after jump to $\adv$.}
Where
\item The range of authority for 
  \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
  \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
  the two stack capabilities have the same permissions as $c_\stk$
\item $c_{f2}'$ points to the return address in f2's code.
\item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
\item 
W = \;& [0 \mapsto \iota_{\malloc,0}] \\
    & [1 \mapsto \iota^\sta(\perma,\ms_{f2})]\\ 
    & [2 \mapsto \iota^\sta (\perma,\ms_\flag)]\\
    & [3 \mapsto \iota^\sta (\perma,\ms_\link)]\\
    & [4 \mapsto \iota^\nwl_{\start_\adv,\addrend_\adv} (\perma)]\\
    & [5 \mapsto \iota^\sta (\temp,\ms_\stk'|_{[\start_\stk,\start_\stk''-1]})] \\
    & [6 \mapsto \iota^\pwl_{\start_\stk'' + 1, \addrend_\stk} (\temp)]
\lau{The interesting regions here are region 5 and 6. Region 5 governs our private part of the stack whereas region 6 governs the part of the stack we are about to release. I don't think it is strictly needed to make them $\temp$ for this example, but in general it is what we wish to do, so we can revoke them upon return.}

>>>>

\begin{lemma}
  \label{lem:correctness-f2}
  For all $n \in \nats$
  let
  \begin{align*}
    \var{offset-link-flag} & \defeq 2
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\var{offset-link-flag}) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\var{offset-link-flag},\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-\var{offset-link-flag},\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  \end{align*}
  and
  \begin{itemize}
  \item The first address of $\hs_{f2}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f2}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assunptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
  \begin{align*}
    &(\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    &\quad(\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
  \end{align*}
Where 
\[
  m''  \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_\link \uplus 
        \hs_\adv \uplus 
        \ms_\malloc \uplus 
        \ms_\stk' \uplus
        \ms_{\var{frame}}
\]
Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
\begin{itemize}
\item The range of authority for 
  \begin{itemize}
  \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
  \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
  \end{itemize}
  the two stack capabilities have the same permissions as $c_\stk$
\item $c_{f2}'$ points to the return address in f2's code.
\item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
\end{itemize}

\begin{figure}
  \label{fig:f2-stack-before-adv}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   &         \\
   & $\vdots$ \\
\cline{2-2}
$\start_\stk'':$   & $0$\\
\cline{2-2}
$c_\stk',c_\stk'' \rightarrow$   & $c_\stk'$ \\
\cline{2-2}
   & $c_{f2}'$ \\
\cline{2-2}
$c_{\var{prp}} \rightarrow$   & Restore code \\
   & $\vdots$ \\
\cline{2-2}
   & $1$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r |c |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $\updatePcPerm{c_\adv}$\\
\cline{2-2}
$r_0$  &  $c_{\var{prp}}$ \\
\cline{2-2}
$r_1$ & $c_\adv$ \\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}'$ \\
\cline{2-2}
& $0$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{Stack and register-file just after jump to $\adv$.}
\end{figure}
Define 
\begin{enumerate}
\item 
  \begin{align*}
W = \;& [0 \mapsto \iota_{\malloc,0}] \\
    & [1 \mapsto \iota^\sta(\perma,\ms_{f2})]\\ 
    & [2 \mapsto \iota^\sta (\perma,\ms_\flag)]\\
    & [3 \mapsto \iota^\sta (\perma,\ms_\link)]\\
    & [4 \mapsto \iota^\nwl_{\start_\adv,\addrend_\adv} (\perma)]\\
    & [5 \mapsto \iota^\sta (\temp,\ms_\stk'|_{[\start_\stk,\start_\stk''-1]})] \\
    & [6 \mapsto \iota^\pwl_{\start_\stk'' + 1, \addrend_\stk} (\temp)]
  \end{align*}
\lau{The interesting regions here are region 5 and 6. Region 5 governs our private part of the stack whereas region 6 governs the part of the stack we are about to release. I don't think it is strictly needed to make them $\temp$ for this example, but in general it is what we wish to do, so we can revoke them upon return.}
\end{enumerate}
